---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# STAT545CountMissing package

<!-- badges: start -->
<!-- badges: end -->

The goal of STAT545CountMissing is to count the number of missing values by group. This package contains one function named `count_all_missing_by_group`, where user can count the number of missing values with the option of displaying by group.

## Installation

You can install the development version of STAT545CountMissing from [GitHub](https://github.com/) with:

``` r
devtools::install_github("stat545ubc-2025/STAT545CountMissing")
```

## Example
### Example 1
This is a basic example which shows you how to solve a common problem. We use the `airquality` dataset and count the number of missing values group by `Month`.

```{r example}
library(STAT545CountMissing)
library(palmerpenguins)
library(tidyverse)
count_all_missing_by_group(airquality, Month)
```

### Example 2

The following example shows how pipe works with this function. All settings are the same as above.

```{r}
airquality |> count_all_missing_by_group(Month)
```


### Example 3

The final example shows the role of `.groups`, which let user to  keep the output grouped by the grouping columns.
```{r}
count_all_missing_by_group(airquality, Month, .groups = "keep")
```

