---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# STAT545CountMissing package

<!-- badges: start -->
<!-- badges: end -->

The goal of STAT545CountMissing is to count the number of missing values by group.

## Installation

You can install the development version of STAT545CountMissing from [GitHub](https://github.com/) with:

``` r
devtools::install_github("Nanboy-Ronan/STAT545CountMissing")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(STAT545CountMissing)
library(palmerpenguins)
library(tidyverse)
count_all_missing_by_group(airquality, Month)
```
The following example shows how pipe works with this function.

```{r}
airquality |> count_all_missing_by_group(Month)
```

The final example shows the role of `.groups`, which let usre to  keep the output grouped by the grouping columns.
```{r}
count_all_missing_by_group(airquality, Month, .groups = "keep")
```

